---
title: "relauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
library(kableExtra)
library(broom.mixed)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
```



# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models. 

```{r}
data <- data %>%
  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>%  
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('relauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```


```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```


# Significance

The following frames are significant: 

* 0:
* 0.01:
* 0.05: abortion regret (+)
* 0.10: evidence (+)
* 0.20: bad law (+), women's health (+)


\newpage

# Abortion Regret


```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))


tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod3)
```


\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod4)
```


\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod9)
```

\newpage 

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod12)
```


\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod18)
```


\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod20)
```


\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod24)
```


\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod27)
```