---
title: "Amicus Word Count"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(tidytext)
library(conText)

# data
# data/processed amicus files/shortened-amicus-brief-text.csv
amicus <- box_read("880862059511")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
```

# Purpose

To pare down amicus text by removing unnecessary/irrelevant text.

1) Remove text AFTER "Summary of Argument" keyword.

2) Remove text AFTER "Appendix" keyword

# Remove after "Summary of Argument"

For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document. This represents the point at which the brief starts discussing their argument. We don't need text prior to this, as it's mainly intro information about the case and/or the authors. If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.

alternate removal strings

```{r}
alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done)

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>% 
  mutate(txt_full = str_to_lower(txt_full),
         txt_full = str_squish(txt_full),
         txt_short = case_when(
           grepl("summary of argument", txt_full) ~ 
             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
           grepl("summary of the argument", txt_full) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", x = txt_full),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           T ~ ""),
         txt_short = str_squish(txt_short))
```

Check none are missed 

```{r}
amicus %>% filter(txt_short == "") %>% select(-txt_full)
```

Check a few by running this line a few times.

```{r}
#amicus %>% sample_n(1) %>% pull(txt_short)
```


# Check instances of "Appendix" or "Footnotes"


Use footnotes when present. If not footnotes, use appendix. If neither: check. There are 154 docs with neither


```{r}
amicus_ends <- amicus %>%
  mutate(appendix = str_count(txt_short, "appendix"),
         appendices = str_count(txt_short, "appendices"),
         footnotes = str_count(txt_short, "footnotes"))

amicus_ends <- amicus_ends %>% select(case, brief, id, appendix, footnotes)
  
#box_write(amicus_ends,
#          file_name = "amicus appendix and footnotes counts.csv",
#          dir_id = 145990409196)
```

# Remove appendices instances

From undergrad assistant: "I have found that often, the appendix will start with an asterisk (usually *1A Appendix). The Appendix also almost always immediately precedes the footnotes."

We need to:

1. find instances of "*1A Appendix" in the text 
2. Check that this only occurs 1x in a doc. 
3a. If 2) is true, then remove text after these instances.
3b. If 3) is false, further inspect the text (may require manual removal)
4. If it does not occur at all, check for the marker for footnotes (see next section). 
5a. If footnote marker exists, remove all text after
5b. If footnote marker does not exist, then manually inspect text. If there are footnotes/appendix, insert flag into text: "MNOPQRST" (w/o quotes) and remove all text after that flag. 


```{r}
brief_names <- amicus %>% 
  arrange(case,brief) %>% 
  mutate(docname = paste0("text", 1:n())) %>%
  select(brief, id, docname)

# remove punctuation
amicus <- amicus %>% 
  arrange(case, brief) %>% 
  mutate(txt_short_clean = gsub("[^[:alpha:][:space:][:digit:]]", " ", txt_short),
                            txt_short_clean = str_squish(txt_short_clean))

# get context around "footnotes"
appendix_context <- get_context(x = amicus$txt_short, target = "appendix", 
                                 window = 5, valuetype = "fixed",
                                 case_insensitive = T, hard_cut = F, verbose = F)

appendix_context <- brief_names %>%
  left_join(., appendix_context, by = "docname")
```

Look for *1a

```{r}
appendix_context %>% filter(grepl("* 1a", context))
```

```{r}
amicus %>% filter(grepl("\\* 1a appendix|*", txt_short)) #%>% select(brief)
```


# Remove footnotes instances

First, get context around "footnotes" 

```{r}
# context function changes brief names to "textN" 
# create this var here so we can map files back
brief_names <- amicus %>% 
  arrange(case,brief) %>% 
  mutate(docname = paste0("text", 1:n())) %>%
  select(brief, id, docname)

# remove punctuation
amicus <- amicus %>% 
  arrange(case, brief) %>% 
  mutate(txt_short_clean = gsub("[^[:alpha:][:space:][:digit:]]", " ", txt_short),
                            txt_short_clean = str_squish(txt_short_clean))

# get context around "footnotes"
footnotes_context <- get_context(x = amicus$txt_short_clean, target = "footnotes", 
                                 window = 5, valuetype = "fixed",
                                 case_insensitive = T, hard_cut = F, verbose = F)
```


Cases where "footnotes" actually references footnotes section, by intuition and some manual inspection:
* footnotes 1
* footnotes counsel of record

```{r}
footnotes_confirmed <- brief_names %>%
  left_join(., footnotes_context, by = "docname") %>%
  select(-target) %>%
  mutate(footnotes_true = ifelse(grepl(" 1 ", context) |
                                   grepl("counsel of record", context),
                                 1, 0)) %>%
  filter(footnotes_true == 1)

footnotes_confirmed %>% distinct(id) %>% nrow()
```

No footnotes:

```{r}
amicus %>% filter(!grepl("footnotes", txt_short)) %>% nrow()
```

Remaining cases: note that this df can have multiple instances of the same case if more than one instance of "footnotes" found.


```{r}
footnotes_tbd <- brief_names %>%
  left_join(., footnotes_context, by = "docname") %>%
  # remove instances of confirmed footnotes (n = 398)
  filter(!(id %in% footnotes_confirmed$id)) %>% 
  # remove instances where "footnotes" not found (n = 270)
  filter(!is.na(context))
```


Save this file for checking:

```{r}
#box_write(footnotes_tbd, file_name = "briefs to check footnotes.xlsx", dir_id = 145990409196)
```



# Save

Original text saved, just added new txt_short col 

```{r}
amicus <- amicus %>% select(-txt_full)
amicus %>% colnames
```


```{r}
#box_write(amicus,
#          file_name = "shortened-amicus-brief-text.csv",
#          dir_id = 145990409196)
```
