---
title: "Top 10 Words by Frame"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)

# data
# data/labeled amicus/amicus_label_density/framing_dictionary.csv
frame_dict <- box_read("914901620274")

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")
```

The purpose of this file is to find the top 10 most common words for each frame list below.

```{r}
search_terms <- c("abortionNegativeII", "actor_couple", "actor_fetus", "actor_physician", "compulsoryII", "compulsoryMotherhood", "evidence experts II", "evidence_uncertainty", "evidence_med_authority", "evidence_research", "evidence_reveal", "evidence_uncertainty", "favorChildbirth", "health", "intersectionality", "law_undueBurdenII", "law_womanRights", "morality", "psy_harm", "womanCitizenship")

frame_dict <- frame_dict %>% filter(code %in% search_terms)
```

Here I iterate through all the words in the frame dictionary and count the number of times they show up in the corpus. I then add this count as a column to the frame dictionary.

```{r}
counts <- c()
for (i in 1:nrow(frame_dict)){
  count <- sum(str_count(amicus$text, frame_dict$word_cleaned[i]))
  counts <- append(counts, count)
}

frame_dict <- cbind(frame_dict, counts)
```

Here I gather the top 10 most common words for a frame a put them in a dataframe.

```{r}
df <- data.frame(matrix(ncol = 2, nrow = 0))
x <- c("frame", "word_cleaned")
colnames(df) <- x


for (term in search_terms){
  top10 <- frame_dict %>% filter(code == term) %>% arrange(desc(counts)) %>% slice(1:10) %>% select(frame = code, word_cleaned)
  df <- rbind(df, top10)
}
```

Now I format the dataframe so that the most common words are in a list.

```{r}
df <- df %>% group_by(frame) %>% summarise(word_list = toString(word_cleaned))
```

Save as a csv.

```{r}
#box_write(df,
#           file_name = "common-words-by-frame.csv",
#           dir_id = 158755083103)
```


