---
title: "Generate Frame Measures"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)
library(tidyverse)
library(tidytext)
library(textclean)
library(tm)
library(stringi)
library(quanteda)

library(boxr)
box_auth()
```


# Purpose

To develop litigant- and frame-level measures of frame usage

# Data

Abortion frame terms:

```{r}
frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
```

Litigant data:

```{r}
# data/processed litigant files/clean-shortened-litigant-brief-text.csv
litigant <- box_read("955397555840") %>% 
  mutate(id = as.character(id)) %>% 
  mutate(brief_party = ifelse(id %in% c("955405762992", "199347141448", "56697932358", "296368043832"), 1, brief_party))
```


# Litigant-Level Measures

Start by creating corpus 


```{r}
litigant_corp <- litigant$text_clean %>% corpus()

# Add meta data to corpus
docvars(litigant_corp, "case") <- litigant$case
docvars(litigant_corp, "brief") <- litigant$brief
docvars(litigant_corp, "id") <- litigant$id
docvars(litigant_corp, "brief_party") <- litigant$brief_party

summary(litigant_corp) %>% head()
```


## Create frame dictionary

This dictionary will be used to filter out frame words from paragraphs when counting word frequency. 

```{r}
# Remove duplicates
frame_terms <- frame_terms %>%
  select(frame_code, word_clean) %>% 
  unique()

# Get words associated with frames
get_frames <- function(frame){ 
  frame_terms %>%
    filter(frame_code == frame) %>% 
    select(word_clean)
  }

# Initialize list
search_frames <- list()

# Get unique frames
frames <- unique(frame_terms$frame_code)

# Pull words for each frame and save in list
for(i in 1:length(frames)){ 
  search_frames[i] <- get_frames(frames[i])
}

# Name items in list
names(search_frames) <- frames

frame_dict <- dictionary(search_frames)

# Check output
#frame_dict
```

# Look up frames

**Note on arguments in `tokens()` function**: removing punctuation and numbers from terms increases counts. 

```{r}
# Tokenize briefs
toks <- tokens(litigant_corp, remove_punct = TRUE, remove_numbers = TRUE)
```

## Create brief summary statistics

The `litigant_corp_summary` data frame contains the summary statistics of all the briefs in our corpus, `litigant_corp`. The one thing it's missing is the number of tokens (i.e. words) in each brief. 

```{r}
# Generate summary of litigantCorp
litigant_corp_summary <- summary(object = litigant_corp, 
                      n = nrow(litigant), # default is 100, we need all observations 
                      showmeta = TRUE) %>% # add meta data to summary
  as.data.frame() 

# check
tail(litigant_corp_summary)
```


Calculate total number of words in each brief. Join with the litigant_corp_summary

```{r}
# Total number of tokens (before pulling frame words)
nToks <- data.frame(Text = names(ntoken(toks)), 
                     word_ct = ntoken(toks))

# Look at first 6 observations
head(nToks)
```

```{r}
litigant_info <- litigant_corp_summary %>%
  left_join(nToks, by = c("Text")) %>% 
  rename(doc_id=Text)

head(litigant_info)
```

## Generate frame frequencies

Now that we've created our `litigant_info` data frame, it's time to generate the frame frequencies.

(# of words/phrases for a particular frame) / (# of all words in the brief)


```{r}
# Search for frames
litigant_dfm <- tokens_lookup(toks, dictionary = frame_dict, nested_scope = "dictionary",
                         case_insensitive = FALSE, valuetype = "fixed") %>% dfm()

# Generate raw frequencies
litigant_frames_raw <- litigant_dfm %>%
  convert(to = "data.frame") %>%
  left_join(litigant_info, by = "doc_id") %>% 
  janitor::clean_names()

# Check out first 6 observations 
head(litigant_frames_raw, 10)
```

Get frame frequencies - These are calculated by dividing the frame count by the word count. 

```{r}
# Generate frame frequencies 
litigant_frames_freq <- litigant_frames_raw %>% 
  pivot_longer(c(abortion_different:womens_rights),
               names_to = "frame", values_to = "frame_ct") %>% 
  mutate(frame_freq = frame_ct/word_ct) %>% 
  select(-frame_ct, -word_ct) %>% 
  pivot_wider(names_from = "frame", values_from = frame_freq)

litigant_frames_freq %>% head(10)
```

## Raw counts + freq

Dataframe with raw counts and frequencies

```{r}
litigant_frames <- litigant_frames_raw %>% 
  select(doc_id:womens_rights, word_ct) %>% 
  left_join(., litigant_frames_freq, 
            by = c("doc_id"), 
            suffix = c("_raw", "_freq")) %>% 
  select(-c(types:sentences)) %>% 
  select(case:brief_party, word_ct, sort(colnames(.))) %>% 
  janitor::clean_names()

litigant_frames %>% head(10)
```

Save

```{r}
box_write(litigant_frames,
           file_name = "litigant-level-frame-measures.csv",
           dir_id = 162601154573)
```



# Case-Level Measures

We already have case-level measures. Just reorganize data for one row per case

```{r}
fem_frames <- litigant_frames %>% filter(brief_party == 1) %>% 
  rename_with(., .fn = ~ paste0("fem_", .x), contains("freq")|contains("raw")) %>% 
  select(case, contains("fem"))
opp_frames <- litigant_frames %>% filter(brief_party == 0) %>% 
  rename_with(., .fn = ~ paste0("opp_", .x), contains("freq")|contains("raw")) %>% 
  select(case, contains("opp"))

case_frames <- fem_frames %>% full_join(., opp_frames, by = "case")
```



Save

```{r}
box_write(case_frames,
           file_name = "case-level-frame-measures.csv",
           dir_id = 162601154573)
```



