---
title: "Amicus Structure"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip?
library(tidyverse)
```


# Purpose

To identify which of the amicus briefs follow the structure below:

Summary of (the) argument

Introductory statement

Statement of (the) case

Interest of (the) amici/amicus/amicus curiae (we’re hoping to exclude this section)

Purpose of the motion

Questions presented

Argument (where this is the only word on the line)

# One Example

After some trial and error, below is how we should process the text and search for the phrases of interest. NOte that Box reads in files line by line, so we are able to search individual lines for each phrase. 

```{r}
id <- '861820915273'

txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_pdf(x)
    )

#txt_full <- paste(txt, sep = ' ', collapse = ' ')

#txt <- gsub('[[:punct:]]','', txt)
txt <- gsub('\\*.', '', txt)
txt <- str_replace_all(txt, "[^a-zA-z]", replacement = "")
txt <- tolower(txt)

"introductorystatement" %in% txt
"summaryofargument" %in% txt
"summaryoftheargument" %in% txt
"argument" %in% txt
"statementofcase" %in% txt
"statementofthecase" %in% txt
"statementsofinterestofamicuscuriae" %in% txt
"interestofamici" %in% txt
"interestoftheamici" %in% txt
"interestofamicus" %in% txt
"interestoftheamicus" %in% txt
"interestofamicuscuriae" %in% txt
"interestoftheamicuscuriae" %in% txt
"purposeofthemotion" %in% txt
"questionspresented" %in% txt
```

# Read in all files, process & search for phrases

Read in amicus file ids csv

```{r}
amicus_ids <- box_read("864720529825")
amicus_ids <- amicus_ids %>% filter(!is.na(id))
amicus_ids %>% head(5)
```


Break up into smaller sections 

Search for phrases:

```{r}
# create iterator 
itd <- iter(amicus_ids, by = "row")

# set up cluster
n_cores <- detectCores() - 1
registerDoParallel(n_cores)

# get text of cases in parallel
amicus_structure <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {
  
  # get id and file type of current file
  id <- i %>% pull(id)
  type <- i %>% pull(file_type)
  
  # grab case and brief names
  case <- i %>% pull(case)
  brief <- i %>% pull(name)
  
  cat(case)
  cat("\t brief started:", brief)
  
  if (type == "pdf") {
    # is the file a PDF
    
    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        pdftools::pdf_text(x) %>%
        readr::read_lines()
    )
    
  } else if (type == "docx") {
    # is the file a DOCX
    
    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_docx(x)
    )
    
  }  else {
    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_document(x)
    )
    
  }
  
  cat("\t \t text read")
  
  # clean
  txt <- gsub('\\*.', '', txt)
  txt <- str_replace_all(txt, "[^a-zA-z]", replacement = "")
  txt <- tolower(txt)

  # search
  intro <- "introductorystatement" %in% txt
  summary <- ifelse("summaryofargument" %in% txt|"summaryoftheargument" %in% txt, T, F)
  argument <- "argument" %in% txt
  statement <- ifelse("statementofcase" %in% txt|"statementofthecase" %in% txt, T, F)
  interest <- ifelse("statementsofinterestofamicuscuriae" %in% txt |
                       "interestofamicuscuriae" %in% txt |
                       "interestoftheamicuscuriae" %in% txt |
                       "interestofamici" %in% txt |
                       "interestoftheamici" %in% txt |
                       "interestofamicus" %in% txt |
                       "interestoftheamicus" %in% txt, T, F)
  purpose <- "purposeofthemotion" %in% txt
  question <- "questionspresented" %in% txt
  
  cat("\t \t phrases found")
  cat("\t \t brief finished")
  
  # add row
  data.frame(case, brief, id, intro, summary, argument, statement, interest, purpose, question)
}

doParallel::stopImplicitCluster()
```


Save to Box

```{r}
box_write(amicus_structure, "amicus structure.xlsx", dir_id = "145990409196")
```


# Check

The main vars we are interested in are "interest" and "summary". Between these two headings is information about the interests of amicus brief authors that we want to remove.

From the first pass, we see that 244 documents have both the interest and summary sections and 103 are missing both. 

```{r}
amicus_structure %>% 
  select(case, brief, interest, summary) %>% 
  group_by(interest, summary) %>% 
  summarize(n = n())
```

Individually check some that are missing "interest". Are there some cases where the formatting/langauge is just different? It's bc they are pdfs and pdfs don't read in line-by-line :(

```{r}
amicus_structure %>% filter(!interest) %>% group_by(case) %>% summarize(n = n()) %>% arrange(-n)
```

# Backup - grepl in text to search for phrases

We can search for all phrases except "argument" by itself

```{r}
amicus <- box_read("863216279471")
```


Search for phrases using grepl: 

```{r}
amicus <- amicus %>%
  mutate(txt_full = tolower(txt_full),
         txt_full = str_squish(txt_full)) %>% 
  mutate(intro = grepl("introductory statement", txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full),
         interest = grepl("interest of amicus|interest of the amicus|interest of amici|interest of the amici", txt_full),
         statement = grepl("statement of case|statement of the case", txt_full),
         purpose = grepl("purpose of the motion", txt_full),
         question = grepl("questions presented", txt_full))

amicus_summary <- amicus %>% 
  select(-txt_full)

amicus_summary %>% head(5)
```


Add to Box

```{r}
box_write(amicus_summary, "amicus summary.xlsx", dir_id = "145990409196")
```


check results - most briefs have summary and interest 

```{r}
amicus_summary %>% select(intro:question) %>% summarize(across(.fns = ~ sum(., is.na(.), 0)))
```
Check co-occurrence - Most briefs have "summary" and "interest" sections (517). 

```{r}
amicus_summary %>% group_by(summary, statement) %>% summarize(n = n())
```



Which briefs don't have "summary" ? 

```{r}
amicus_summary %>% filter(!summary) %>% group_by(case) %>% summarize(n = n()) %>% arrange(-n)
```

```{r}
amicus_summary %>% filter(case == "Harris v. McRae", !summary)
```

