---
title: "VIF"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F, error=F)

library(tidyverse)
library(lme4)
library(boxr)
library(kableExtra)
library(broom.mixed)
library(performance)
```

# Data

Regression data used in models

```{r}
data <- #box_read(final_cases) %>% 
  read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(forgauf_abortion_regret:forgauf_womens_health,
                  legauf_abortion_regret:legauo_womens_health,
                  lifauo_abortion_regret:medauo_womens_health,
                  relauf_abortion_regret:relauo_womens_health,
                  fem_abortion_regret:opp_womens_health),
                ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")

# scale
data <- data %>%
  select(case:cirsplit, pfemam, poppam,
         forgauf_abortion_regret:forgauf_womens_health,
         legauf_abortion_regret:legauo_womens_health,
         lifauo_abortion_regret:medauo_womens_health,
         relauf_abortion_regret:relauo_womens_health,
         fem_abortion_regret:opp_womens_health) %>%  
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
```

# Models

VIF for each frame X amici type

## Feminist-org

Abortion regret 

```{r}
mod_forg_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_1)

#qqnorm(resid(mod_forg_1))
```


Expert evidence

```{r}
mod_forg_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_2)
```

Fetus

```{r}
mod_forg_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_3)
```

Morality & religion

```{r}
mod_forg_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_4)
```


Privacy

```{r}
mod_forg_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_5)
```


Undue burden

```{r}
mod_forg_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_6)
```


Women's futures

```{r}
mod_forg_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_7)
```


Women's health

```{r}
mod_forg_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_8)
```

## Medical (RR)

Abortion regret 

```{r}
mod_medRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                medauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_1)
```


Expert evidence

```{r}
mod_medRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_2)
```

Fetus

```{r}
mod_medRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_3)
```

Morality & religion

```{r}
mod_medRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_4)
```


Privacy

```{r}
mod_medRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_5)
```


Undue burden

```{r}
mod_medRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_6)
```


Women's futures

```{r}
mod_medRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                medauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_7)
```


Women's health

```{r}
mod_medRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_8)
```

## Legal (RR)

Abortion regret 

```{r}
mod_legRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_1)
```


Expert evidence

```{r}
mod_legRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_2)
```

Fetus

```{r}
mod_legRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_3)
```

Morality & religion

```{r}
mod_legRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_4)
```


Privacy

```{r}
mod_legRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_5)
```


Undue burden

```{r}
mod_legRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_6)
```


Women's futures

```{r}
mod_legRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_7)
```


Women's health

```{r}
mod_legRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_8)
```

## Religious (RR)

Abortion regret 

```{r}
mod_relRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                relauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_1)
```


Expert evidence

```{r}
mod_relRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_2)
```

Fetus

```{r}
mod_relRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_3)
```

Morality & religion

```{r}
mod_relRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_4)
```


Privacy

```{r}
mod_relRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_5)
```


Undue burden

```{r}
mod_relRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_6)
```


Women's futures

```{r}
mod_relRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                relauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_7)
```


Women's health

```{r}
mod_relRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_8)
```


## Prolife-orgs

Abortion regret 

```{r}
mod_lif_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                lifauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_1)
```


Expert evidence

```{r}
mod_lif_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_2)
```

Fetus

```{r}
mod_lif_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_3)
```

Morality & religion

```{r}
mod_lif_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_4)
```


Privacy

```{r}
mod_lif_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_5)
```


Undue burden

```{r}
mod_lif_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_6)
```


Women's futures

```{r}
mod_lif_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                lifauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_7)
```


Women's health

```{r}
mod_lif_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_8)
```

## Medical (AA)

Abortion regret 

```{r}
mod_medAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                medauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_1)
```


Expert evidence

```{r}
mod_medAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_2)
```

Fetus

```{r}
mod_medAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_3)
```

Morality & religion

```{r}
mod_medAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_4)
```


Privacy

```{r}
mod_medAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_5)
```


Undue burden

```{r}
mod_medAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_6)
```


Women's futures

```{r}
mod_medAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                medauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_7)
```


Women's health

```{r}
mod_medAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_8)
```

## Legal (AA)

Abortion regret 

```{r}
mod_legAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_1)
```


Expert evidence

```{r}
mod_legAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_2)
```

Fetus

```{r}
mod_legAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_3)
```

Morality & religion

```{r}
mod_legAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_4)
```


Privacy

```{r}
mod_legAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_5)
```


Undue burden

```{r}
mod_legAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_6)
```


Women's futures

```{r}
mod_legAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_7)
```


Women's health

```{r}
mod_legAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_8)
```


## Religious (AA)

Abortion regret 

```{r}
mod_relAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                relauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_1)
```


Expert evidence

```{r}
mod_relAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_2)
```

Fetus

```{r}
mod_relAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_3)
```

Morality & religion

```{r}
mod_relAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_4)
```


Privacy

```{r}
mod_relAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_5)
```


Undue burden

```{r}
mod_relAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_6)
```


Women's futures

```{r}
mod_relAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                relauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_7)
```


Women's health

```{r}
mod_relAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_8)
```
